An Intrinsically-Typed Solution for the\\ List-Machine Benchmark

### 2021-03-09 papers/COLA/paper.tex
Little modifications on text

>>>>

The modifications on the subtyping and least upper bound induced changes on all theorems
about these relations. On our first implementation, these results are just straightforward
inductive proofs. Because of the mutually inductive nature of the new relation versions, all
these proofs needed to be defined by mutually recursive functions.
